In-silico molecular enrichment and clearance of the human intracranial space

### 2025-03-20 paper/main.tex
Updates from Overleaf

\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{float}
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{placeins}
\usetikzlibrary{quotes}
\usetikzlibrary{arrows,decorations.pathmorphing,backgrounds,positioning,fit,petri}

@@

\flushbottom
\maketitle

@@

% Limitations
In terms of limitations, our primary constraint modelling-wise is the
geometric representation of the vascular (and therefore also
perivascular) networks. Concretely, we account for no vessels below
the original MRI resolution limits, and thus only a part of the
cerebral surface vasculature and effectively not the cortical
vessels. In addition, and again due to lack of resolution, there is
uncertainty associated with the location of the vessel segments
relative to the CSF spaces and parenchyma, with some vessels
surrounded by both domains and some vessels completely entering the
parenchyma before returning to the SAS. Higher resolution MRI data
(T1w and e.g. time-of-flight, QSM or other modalities) in more
subjects would immediately allow for more detailed studies of this
aspect. As a result of the lack of an accurate representation of the
cortical and subcortical white matter vasculature, we have considered
a conservative transport model within the parenchyma, modelling
extracellular diffusion alone. To compensate, we have focused on
reporting detailed predictions in the CSF spaces and surface PVS after
not more than 24 hours. In particular, we note that, we observe tracer
accumulation at the perivascular network ends after 12 hours,
similar to that previously observed for
microspheres~\cite{bedussi2018paravascular, mestre2018flow}, which
here can be interpreted as an artifact of the incomplete network
creating up a barrier for tracer movement. Previously, we have found
that enrichment within the parenchyma is well-represented by $\approx
3\times$ enhanced diffusion augmented by local clearance e.g.~across
the blood-brain barrier or diffusion-convection with a complex pattern
of spatially-varying convective velocities of 1-10 \textmu
m/min~\cite{vinje2023human}. We will incorporate such transport
mechanisms within the parenchyma in future work. Finally, we also note
that we simulate the intracranial distribution of a tracer
concentration appearing at the craniocervical junction rather than as
an intrathecal injection. We therefore overestimate the amount of
tracer entering into the intracranial spaces; however, due to the
linearity of the mathematical model, it is valid to directly interpret
the in-silico concentrations relative to the total amount of tracer.

% Outlook
In conclusion, our findings transfer insights from experimental
studies and theoretical analysis to the in-silico human setting,
reconcile seemingly conflicting observations in particular relating to
directionality of perivascular flow, and integrate different physical
mechanisms across across spatial and temporal scales. The complete
simulation pipeline is openly available, including interactive
visualization of simulation results for all model
variations~\cite{ZENODO}. Looking ahead, this platform establishes a
foundation for in-silico studies of molecular movement within the
human brain environment, such as tailored predictions of intrathecal
chemotherapy delivery or personalized diagnostics of brain clearance
capacity.

>>>>

\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{float}
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{placeins}
\usepackage{lineno}
\usetikzlibrary{quotes}
\usetikzlibrary{arrows,decorations.pathmorphing,backgrounds,positioning,fit,petri}

@@

\linenumbers

\flushbottom

\maketitle

@@

% Limitations
In terms of limitations, our primary constraint modelling-wise is the
geometric representation of the vascular (and therefore also
perivascular) networks. Concretely, we account for no vessels below
the original MRI resolution limits, and thus only a part of the
cerebral surface vasculature and effectively not the cortical
vessels. In addition, and again due to lack of resolution, there is
uncertainty associated with the location of the vessel segments
relative to the CSF spaces and parenchyma, with some vessels
surrounded by both domains and some vessels completely entering the
parenchyma before returning to the SAS. Higher resolution MRI data
(T1w and e.g. time-of-flight, QSM or other modalities) in more
subjects would immediately allow for more detailed studies of this
aspect. As a result of the lack of an accurate representation of the
cortical and subcortical white matter vasculature, we have considered
a conservative transport model within the parenchyma, modelling
extracellular diffusion alone. To compensate, we have focused on
reporting detailed predictions in the CSF spaces and surface PVS after
not more than 24 hours. In particular, we note that, we observe tracer
accumulation at the perivascular network ends after 12 hours,
similar to that previously observed for
microspheres~\cite{bedussi2018paravascular, mestre2018flow}, which
here can be interpreted as an artifact of the incomplete network
creating a barrier for tracer movement. Previously, we have found
that enrichment within the parenchyma is well-represented by $\approx
3\times$ enhanced diffusion augmented by local clearance e.g.~across
the blood-brain barrier or diffusion-convection with a complex pattern
of spatially-varying convective velocities of 1-10 \textmu
m/min~\cite{vinje2023human}. We will incorporate such transport
mechanisms within the parenchyma in future work. Finally, we also note
that we simulate the intracranial distribution of a tracer
concentration appearing at the craniocervical junction rather than as
an intrathecal injection. We therefore overestimate the amount of
tracer entering into the intracranial spaces; however, due to the
linearity of the mathematical model, it is valid to directly interpret
the in-silico concentrations relative to the total amount of tracer.

% Outlook
In conclusion, our findings transfer insights from experimental
studies and theoretical analysis to the in-silico human setting,
reconcile seemingly conflicting observations in particular relating to
directionality of perivascular flow, and integrate different physical
mechanisms across spatial and temporal scales. The complete
simulation pipeline is openly available, including interactive
visualization of simulation results for all model
variations~\cite{ZENODO}. Looking ahead, this platform establishes a
foundation for in-silico studies of molecular movement within the
human brain environment, such as tailored predictions of intrathecal
chemotherapy delivery or personalized diagnostics of brain clearance
capacity.
